Some supplements

### 2020-02-02 ICML/chanwoo/Supplements.tex
Add files via upload

>>>>

\section{Brain data clustering}

\begin{table}[]
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Group       & \multicolumn{3}{c|}{\#1}                                                  & \multicolumn{3}{c|}{\#2}                                      \\ \hline
Brain nodes & \multicolumn{3}{l|}{\begin{tabular}[c]{@{}l@{}}"RMF\_L","Fpole\_L","Insula\_L",\\ "SupF\_L","CaudMF\_L",\\ "parsTriangularis\_L","parsOpercularis\_L",\\ "preCentral\_L","Tpole\_L","SupT\_L",\\ "SupT\_L","postCentral\_L", "SupP\_L",\\ "IP\_L","LO\_L","MOF\_L","SupF\_L",\\ "IsthmusC\_L","Precuneus\_L",\\ "Cuneus\_L","paraHippo\_L",\\ "Lingual\_L","SupT\_L","LO\_L"\end{tabular}} & \multicolumn{3}{l|}{\begin{tabular}[c]{@{}l@{}}"RMF\_R","Fpole\_R","Insula\_R",\\ "SupF\_R", "CaudMF\_R",\\ "parsTriangularis\_R" ,"parsOpercularis\_R",\\ "preCentral\_R", "Tpole\_R","SupT\_R",\\ "SupT\_R","postCentral\_R","SupP\_R",\\ "IP\_R","LO\_R","MOF\_R", "SupF\_R",\\ "IsthmusC\_R","Precuneus\_R",\\ "Cuneus\_R","paraHippo\_R",\\ "Lingual\_R","SupT\_R","LO\_R"\end{tabular}} \\ \hline
Group       & \#3    & \#4    & \#5   & \#6  & \#7 & \#8
\\ \hline
Brain nodes & \begin{tabular}[c]{@{}c@{}}"SupraM\_L" \\ "SupraM\_L" \\ "SupraM\_L" \\ "SupraM\_L"\end{tabular}                                      & \begin{tabular}[c]{@{}c@{}}"SupraM\_R" \\ "SupraM\_R" \\ "SupraM\_R" \\ "SupraM\_R"\end{tabular}                                      & \begin{tabular}[c]{@{}c@{}}"IT\_L" \\ "IT\_L" \\ "IT\_L"\end{tabular}                                      & \begin{tabular}[c]{@{}c@{}}"IT\_R" \\ "IT\_R" \\ "IT\_R"\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}"MT\_L" \\ "MT\_L" \\ "MT\_L"\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}"MT\_R" \\ "MT\_R"\\ "MT\_R"\end{tabular}                                                         \\ \hline
\end{tabular}
\end{table}
\begin{figure}[H]
  \centering
 \includegraphics[width = 0.45\textwidth]{elbowmethod.png}

  \label{figure:cluster graph}
  \caption{Brain cluster graph}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width = 0.45\textwidth]{brain1.jpg}
 \includegraphics[width = 0.45\textwidth]{brain2.jpg}
 \includegraphics[width = 0.45\textwidth]{brain3.jpg}
 \includegraphics[width = 0.45\textwidth]{brain4.jpg}
  \label{figure:clustering}
  \caption{Brain cluster groups}
\end{figure}
